Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-10-18 paper/main.tex
updated figures
updated paper
new references + new paragraph to discuss spin and vorticity
darfting the abstract

@@

@@

\item
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for alignment of angular momentum vectors with neighbohring
structures or other massive structures. They match halos using close
pair statistics. They do not find any evidence for a statistically
significant mutual alignment of halos on any escale. 
\end{itemize}
\section{N-body simulation and halo finding}

\begin{figure}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/Web.pdf}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/VWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/TWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jVWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/jTWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

\begin{figure*}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWeb.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vVWebV2.pdf}
\includegraphics[width=0.45\textwidth]{../plot2/Mass/vTWebV2.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}

>>>>

We study
the alignment of DM halos with the cosmic web as described by the
tidal and velocity shear fields. We focus on the alignment of halos
shape, spin and peculiar velocities. We use a cosmological N-body
simulation that allows to study dark matter halos spanning four orders
of magnitude in mass ($(10^{10}$-$10^{14}$) \hMsun and spatial
scales of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying
the numerical parameters in our experiments we find that the tidal
field provides a robust description for the different kinds of
alignments.  We measure a strong here is a strong alignment of the
peculiar velocity field and the halo shape with the cosmic web defined
by the tidal field. The results for the spin alignment are less
significant. The shape alignment is stronger for halos that are either
 massive ($M>10^{12}$\hMsun), have large or are located in high
 density regions.

@@

\section{N-body simulation and halo finding}

\begin{figure}
\includegraphics[width=0.40\textwidth]{web.pdf}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig4.pdf}
\caption{Median of $\cos\theta$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and a halo's peculiar
  velocity.} 
\end{figure*}

We do not find a strong signal for the alignment of spin and the
cosmic web. A significant correlation signal has been recently
measured between the spin and the cosmic vorticity
\citep{Libeskind2013a,Laigle2013}. This two facts are consistent with
spin being produced by the non-symmetric part of the shear and tidal
tensors.

\section*{Appendix A. Detailed description of previous theoretical results}

@@

\item
\citep{Lee2002}%Obs. spin alignment
Observational measurement for the alignment of galaxy spin axes with
the local tidal shear field. For the measurement of shear, we have used
the Point Source Catalog Redshift (PSCz) survey (a complete redshift survey
from the IRAS Point Source Catalog) data. This was done down to a
radial comoving distance of $\sim 150$\hMpc.
\item
\citep{Hatton2001} %angular momentum alignment
DM matter only simulation. $256^3$ particles, $100$\hMpc, particle
mass. Look for alignment of angular momentum vectors with neighbohring
structures or other massive structures. They match halos using close
pair statistics. They do not find any evidence for a statistically
significant mutual alignment of halos on any escale. 
\end{itemize}
